Query Optimization for Dynamic Imputation

### 2017-07-09 paper/algorithm.tex
Clarify that attributes not being imputed are ignored if missing

The chained-equation algorithm proceeds by
iteratively fitting decision trees for the target attributes. 
In each iteration, the missing values of a single attribute are replaced with newly imputed values.  Values in a single column can be updated over multiple
iterations of the algorithm. With more iterations, the quality of the
imputation improves as values progressively reflect more accurate relationships
between attributes. The algorithm terminates after a fixed number of
iterations, or earlier if convergence is achieved, indicated by unchanged values in a 
column in subsequent iterations. For our experiments, we use Weka's \texttt{REPTree}
decision tree implementation~\cite{witten2016data}, a variant of the canonical \texttt{C4.5}
algorithm~\cite{quinlan1993}. Roughly, the time complexity of building one
decision tree is $\mathcal{O}(nm \text{ } log(n))$, where $n$ is the number of tuples
and $m$ is the number of dependent attributes~\cite{witten2016data}. Since we build
$k * |\textsc{Dirty}(q)|$ trees, we have
\begin{equation*}
    \begin{aligned}
    T(q) = k * &|\textsc{Dirty}(q)| * \textsc{Card}(q) * \\
               &(|\textsc{Clean}(q)| + |\textsc{Dirty}(q)| - 1) * log(\textsc{Card}(q)).
    \end{aligned}
\end{equation*}

>>>>

The chained-equation algorithm proceeds by
iteratively fitting decision trees for the target attributes. 
In each iteration, the missing values of a single attribute are replaced with newly imputed
values. \cameraready{Attributes that contain missing values but that are not being imputed are
ignored by the imputation.}
Values in a single column can be updated over multiple
iterations of the algorithm. With more iterations, the quality of the
imputation improves as values progressively reflect more accurate relationships
between attributes. The algorithm terminates after a fixed number of
iterations, or earlier if convergence is achieved, indicated by unchanged values in a 
column in subsequent iterations. For our experiments, we use Weka's \texttt{REPTree}
decision tree implementation~\cite{witten2016data}, a variant of the canonical \texttt{C4.5}
algorithm~\cite{quinlan1993}. Roughly, the time complexity of building one
decision tree is $\mathcal{O}(nm \text{ } log(n))$, where $n$ is the number of tuples
and $m$ is the number of dependent attributes~\cite{witten2016data}.
\cameraready{With $k$ cycles of the algorithm, where in each cycle there are
$|\textsc{Dirty}(q)|$ iterations of fitting models for each dirty attribute, we have}
\begin{equation*}
    \begin{aligned}
    T(q) = k * &|\textsc{Dirty}(q)| * \textsc{Card}(q) * \\
               &(|\textsc{Clean}(q)| + |\textsc{Dirty}(q)| - 1) * log(\textsc{Card}(q)).
    \end{aligned}
\end{equation*}
